Testing Education State Transitions

### 2023-06-20 minos/testing/education_transitions.Rmd
Added plots for hh_income and SF12 by education level

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

ggplot(data = raw.meanAge, aes(x = education_state, y = age)) +
  geom_col()

@@

@@

>>>>

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'stock_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

ggplot(data = raw.meanAge, aes(x = education_state, y = age)) +
  geom_col() +
  geom_text(aes(label = format(round(age, 2), nsmall = 2)), vjust = -0.5)

@@

## Summary stats by educ_state

```{r}
raw.by.educ <- raw.dat %>%
  group_by(education_state) %>%
  summarise(hh_income = mean(hh_income, na.rm = TRUE),
            SF12 = mean(SF_12, na.rm = TRUE))

raw.by.educ$education_state <- as.factor(raw.by.educ$education_state)

ggplot(raw.by.educ, aes(x = education_state, y = hh_income)) +
  geom_col()

ggplot(raw.by.educ, aes(x = education_state, y = SF12)) +
  geom_col()
```

## Max Education Predictions

```{r}
raw.maxEduc <- raw.dat %>%
  dplyr::filter(age < 31) %>%
  dplyr::select(pidp, time, age, education_state, max_educ, S7_labour_state)

raw.maxEducDiff <- raw.maxEduc %>%
  dplyr::filter(max_educ != education_state)
```

@@

spaghetti_plot(raw.s, 'education_state',
               save = FALSE)
